# Einleitung {#intro}


You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mfrow = c(1, 2))
plot_call_price(t = 0, S = seq(5, 15, 0.01), r = 0.01, sigma = 0.5, K = 10, T = 0.4, move = 0.2, type = "call")
plot_call_price(t = 0, S = seq(5, 15, 0.01), r = 0.01, sigma = 0.5, K = 10, T = 0.4, move = 0.2, type = "put")
par(mfrow = c(1, 1))
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
